Demographic Predictors of Party Affiliation: Insights from the 2022 Cooperative Election Study

### 2024-03-12 paper/paper.qmd
upload

---
title: "Demographic Predictors of Party Affiliation: Insights from the 2022 Cooperative Election Study"
subtitle: "Examining the Influence of Gender, Race, and Education Level on Political Leanings in the United States"
author: 
  - Sirui Tan
thanks: "Code and data are available at: https://github.com/siru1366/us.git."
date: today
date-format: long
abstract: "Our study investigates the political leanings of American voters, particularly their affiliation with the Democratic and Republican parties, and its relationship with demographic factors. Analyzing data from the 2022 Cooperative Election Study, we utilized logistic regression analysis to identify key predictors of party allegiance. Specifically, our findings indicate that gender, race, and education level strongly influence political leanings, with women, black people, Latinos, and individuals with higher education levels exhibiting a greater tendency to align with the Democratic Party. Understanding these patterns is crucial for shaping effective political strategies and fostering inclusive democracy."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-modelresultsfig
#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

mcmc_intervals(political_preferences, prob = 0.9) +
  labs(x = "90 per cent credibility interval")
```

@@

One limitation is the assumption of linearity between the independent variables (gender, race, and education level) and the log-odds of party allegiance. While logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, leading to potential model misspecification (@agresti2015foundations).Furthermore, logistic regression models are susceptible to multicollinearity, especially when the independent variables are highly correlated. In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable (@allison1999logisti).

>>>>

---
title: "Demographic Predictors of Party Affiliation: Insights from the 2022 Cooperative Election Study"
subtitle: "Examining the Influence of Gender, Race, and Education Level on Political Leanings in the United States"
author: 
  - Sirui Tan
thanks: "Code and data are available at: https://github.com/siru1366/us.git."
date: today
date-format: long
abstract: "Our study investigates the political leanings of American voters, particularly their affiliation with the Democratic and Republican parties, and its relationship with demographic factors. Analyzing data from the 2022 Cooperative Election Study, we utilized logistic regression analysis to identify key predictors of party allegiance. Specifically, our findings indicate that gender, race, and education level strongly influence political leanings, with women, black people, Latinos, and individuals with higher education levels exhibiting a greater tendency to align with the Democratic Party. Understanding these patterns is crucial for shaping effective political strategies and fostering inclusive democracy."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models Political Preferences (n = 5000)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-modelresultsfig
#| fig-cap: "90 percent credibility interval"
#| warning: false

@@

mcmc_intervals(political_preferences, prob = 0.9) 
```

@@

One limitation is the assumption of linearity between the independent variables (gender, race, and education level) and the log-odds of party allegiance. While logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, leading to potential model misspecification (@agresti2015foundations).Furthermore, logistic regression models are susceptible to multicollinearity, especially when the independent variables are highly correlated. In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable (@allison1999logistic).
